\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-25 article.tex
Proof New Screening Test

Fifteen years on and the world has changed, technology is now at the forefront of everything we do, a screening test which requires pen and paper and access to a specialist who owns the required equipment seems outdated. 
With the technology currently available more and more tasks which used to require specialised expertise are becoming available to everyone, accessible in schools, homes, and even on the go. With all this new technology being so readily available one must consider whether there is now a more cost effective and accessible way to screen for dyslexia.

>>>>

Fifteen years on and the world has changed, technology is now at the forefront of everything we do, a screening test which requires pen and paper and access to a specialist who owns the required equipment seems outdated. 
With the technology currently available more and more tasks which previously required specialise expertise are becoming available to everyone. With all this new technology being so readily available one must consider whether there is now a more cost effective and accessible way to screen for dyslexia.
